Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-10 popl24/gmw.tex
checkpoint

\begin{fpfig}[t]{2-Party GMW functions.}{fig-gmw}
{\footnotesize
  \begin{verbatimtab}
    encodegmw(in1,in2)
    {
      v[1, in1 || out] := s[1,in1] xor flip[1,in1];
      v[2, in1 || out] := flip[1,in1];
      v[1, in2 || out] := s[2,in2] xor flip[2,in2];
      v[2, in2 || out] := flip[2,in2]
      { shares1 = { c1 = v[1, in1 || out]; c2 = v[2, in1 || out] };
        shares2 = { c1 = v[1, in2 || out]; c2 = v[2, in2 || out]} } 
    }

@@

    andgmw(g, shares1, shares2)
    {
      let r = flip[1,g || .r] in
      let table = andtablegmw(shares1.c1, shares2.c1) in
      let r11 =  r xor table.v1 in
      let r10 =  r xor table.v2 in
      let r01 =  r xor table.v3 in
      let r00 =  r xor table.v4 in
      v[2,g || out] := OT4(shares1.c2, shares2.c2, r11, r10, r01, r00);
      v[1,g || out] := r;
      { c1 = v[1,g || out]; c2 = v[2,g || out]}
    }

    decodegmw(shares)
    {
      v[0,output] := shares.c1 xor shares.c2
    }
  \end{verbatimtab}
}
\end{fpfig}

>>>>

\begin{fpfig}[t]{2-Party GMW Circuit Library with And gate.}{fig-gmw}
{\footnotesize
  \begin{verbatimtab}
    encodegmw(in1,in2) {
      v[1, in1 || "out"] := s[1,in1] xor flip[1,in1];
      v[2, in1 || "out"] := flip[1,in1];
      v[1, in2 || "out"] := s[2,in2] xor flip[2,in2];
      v[2, in2 || "out"] := flip[2,in2]
      { shares1 = { c1 = v[1, in1 || "out"]; c2 = v[2, in1 || "out"] };
        shares2 = { c1 = v[1, in2 || "out"]; c2 = v[2, in2 || "out"]} } 
    }

@@

    andgmw(g, shares1, shares2) {
      let r = flip[1,g || ".r"] in
      let table = andtablegmw(shares1.c1, shares2.c1) in
      let r11 =  r xor table.v1 in
      let r10 =  r xor table.v2 in
      let r01 =  r xor table.v3 in
      let r00 =  r xor table.v4 in
      v[2,g || "out"] := OT4(shares1.c2, shares2.c2, r11, r10, r01, r00);
      v[1,g || "out"] := r;
      { c1 = v[1,g || "out"]; c2 = v[2,g || "out"]}
    }

    decodegmw(shares) { v[0,"output"] := shares.c1 xor shares.c2 }
  \end{verbatimtab}
}
\end{fpfig}

### 2023-07-10 popl24/metalang.tex
checkpoint

When we consider the examples of GMW and YGC in detail below, our
focus will be on developing a codebase that can be used to define
arbitrary circuits, i.e., complete and concrete protocols. Since
strings and identifiers can be constructed manually, and expressions
can occur inside assignments and boolean expression forms, function
definitions can generalize over $\fedprot$-level patterns to obtain
composable program units. \cnote{Cur the following example to save
  space?.}  As a simple example, consider 3 party secret sharing as
illustrated in Example \ref{example-he}. We can define a function
$\ttt{share3}$ that abstracts the process of splitting a given
client's secret into 3 separate shares.
\begin{example} \label{example-share3} The function $\ttt{share3}$ 
  splits a client's secret into 3 shares returned as a record
  with fields $\ttt{s1-3}$:
  {\small
  \begin{verbatimtab}
      share3(client, secretid) {
        let s1 = flip[client, share1] in
        let s2 = flip[client, share2] in
        let s3 = (s1 xor s2) xor s[client, s: || secretid] in
        {s1 = s1;s2 = s2;s3 = s3}
      } \end{verbatimtab}
  }
  Here is a $\metaprot$ program that uses this function definition:
  {\small
    \begin{verbatimtab}
      let shares = share3(1, mysecret) in
      v[2,s1] := shares.s2;
      v[3,s1] := shares.s3 \end{verbatimtab}
  }
  which generates the following $\minifed$ program, as we formalize in Example \ref{example-share3-eval}
  below:
  {\small
  \begin{verbatimtab}
      v[2,s1] := flip[1, share2];
      v[3,s1] := flip[1, share1] xor flip[1, share2] xor s[1, s:mysecret] \end{verbatimtab}
  }
\end{example}

@@

For full details of the GMW protocol the reader is referred to
\cite{evans2018pragmatic}. Our implementation libary is shown in
Figure \ref{fig-gmw}, with type signatures for the library functions
shown in Figure \ref{fig-gmw-types}. We show the And gate since it is
an interesting component. The Figure includes the
following top-level functions:
\begin{itemize}
\item \ttt{encodegmw}: This function encodes client 1's and client 2's
  secret bits called $\ttt{s[1,s1]}$ and $\ttt{s[1,s2]}$ into two
  distinct wire values (pairs of shares).
\item \ttt{andgmw}: This function defines the gate $\ttt{g}$, the
  identifier $\ttt{g}$ being used to distinguish randomness used
  within.  In our version client 1 builds the output table (using
  \ttt{andtablegmw})and transfers the correct output share to client 2
  using 1-out-of-4 OT as per standard GMW protocol.
\item \ttt{decode}: This function decodes and publishes a wire value
  by $\ttt{xor}$ing the shares. Note that this requires both client 1
  and 2 to publicize their shares.
\end{itemize}
\begin{example}
  \label{example-gmw-andcircuit}
The following program uses our GMW library to define
a circuit with a single And gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively. 
{\small
  \begin{verbatimtab}
  let ss = encodegmw(s1,s2) in v[0,output] := decode(andgmw(0,ss.shares1,ss.shares2))
  \end{verbatimtab}
}
\end{example}

@@

\emph{Wire labels} are fundamental to YGC, and essentially represent
gate output values in an encrypted form. In our definition, wire
labels are represented by records $\ttt{\{ k = }\beta_1\ttt{; p =
}\beta_2\ttt{ \}}$, where $\ttt{k}$ is the \emph{key bit} and
$\ttt{p}$ is the \emph{pointer bit}, and $\beta_1$ and $\beta_2$ are
flips. Flips in each output wire label are owned by the garbler and
are unique per gate by definition of their identifying string, and the
representation of $0$ is the negation of $1$. For example, here is the
representation of 1 and 0 respectively in the output wire label for a
hypothetical gate 6:
{\small
  \begin{mathpar}
    \ttt{\{ k = flip[2,gate:6.k]; p =  flip[2,gate:6.p]] \}}

    \ttt{\{ k = not flip[2,gate:6.k]; p =  not flip[2,gate:6.p]] \}}
  \end{mathpar}
}
In our implementation, gates are wired together using gate
identifiers, which are strings $w$. Top-level functionality
shown in Figure \ref{fig-ygc-lib} includes:
\begin{itemize}
\item \ttt{owl}: This function returns the output wire label for any
  gate identified by \ttt{gid}.
\item \ttt{andgate}: This defines a subprotocol for the garbler
  to define a garbled gate $\ttt{gid}$ with input wires from gates
  $\ttt{ga}$ and $\ttt{gb}$. The garbler generates keys and garbles
  the rows in YGC fashion, them with client $1$ in
  views in a standard form. For example, the view for
  a hypothetical gate 6, row 2 garbled truth table is $\ttt{v[1,gate:6tt2]}$.
  We note that garbled gates of other binary operators can be obtained with
  replacement of $\ttt{andtable}$ with appropriate garbled table definitions. 
\item \ttt{evalgate}: This defines a subprotocol for the evaluator to
  evaluate gate $\ttt{gid}$ given input wire values $\ttt{wva}$ and
  $\ttt{wvb}$.
\item \ttt{andygc}: This composes the garbler and evaluator subprotocols
  for construction and evaluation of an And gate. 
\item \ttt{garbledecode} and \ttt{evaldecode}: The former function
  defines the garbler's protocol for encrypting the circuit
  output from final gate $\ttt{gid}$, and the latter defines
  the evaluator's output decryption protocol. These are composed with \ttt{decodeygc}.
\item \ttt{encodegmw}: This defines the initial phase of the protocol,
  where the evaluator receives the wire value from their own
  secret $\sx{1}{sa}$ via $\ttt{OT}$, and the garbler communicates
  the wire value for their own secret $\sx{2}{sb}$ directly.
\end{itemize}
We provide more code details in Appendix \ref{section-ygc}, Figures
\ref{fig-ygc-aux} and \ref{fig-ygc-gates}, and complete code in our
online repository.
\begin{example}
  \label{example-ygc-andcircuit}
The following program uses our YGC library to define
a circuit with a single and gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively. 
{\small
\begin{verbatimtab}
  let secrets = encode("s1","s2") in
  v[0,output] := decode(andgg("0", secrets.wv1, secrets.wv2)) \end{verbatimtab}
}
%\begin{verbatimtab}
%  andgate(0,s1,s2);
%  garbledecode(0);
%  let secrets = encode(s1,s2) in
%  v[0,output] := decode(evalgate(0, secrets.wv1, secrets.wv2))
%\end{verbatimtab}
\end{example}

>>>>

When we consider the examples of GMW and YGC in detail below, our
focus will be on developing a codebase that can be used to define
arbitrary circuits, i.e., complete and concrete protocols. Since
strings and identifiers can be constructed manually, and expressions
can occur inside assignments and boolean expression forms, function
definitions can generalize over $\fedprot$-level patterns to obtain
composable program units. \cnote{Cur the following example to save
  space?.}  As a simple example, consider 3 party secret sharing as
illustrated in Example \ref{example-he}. We can define a function
$\ttt{share3}$ that abstracts the process of splitting a given
client's secret into 3 separate shares.
\begin{example} \label{example-share3} The function $\ttt{share3}$ 
  splits a client's secret into 3 shares returned as a record
  with fields $\ttt{s1-3}$:
  {\small
  \begin{verbatimtab}
      share3(client, secretid) {
        let s1 = flip[client, "share1"] in
        let s2 = flip[client, "share2"] in
        let s3 = (s1 xor s2) xor s[client, "s:" || secretid] in
        {s1 = s1;s2 = s2;s3 = s3}
      } \end{verbatimtab}
  }
  Here is a $\metaprot$ program that uses this function definition:
  {\small
    \begin{verbatimtab}
      let shares = share3(1, "mysecret") in
      v[2,s1] := shares.s2;
      v[3,s1] := shares.s3 \end{verbatimtab}
  }
  which generates the following $\minifed$ program, as we formalize in Example \ref{example-share3-eval}
  below:
  {\small
  \begin{verbatimtab}
      v[2,s1] := flip[1, "share2"];
      v[3,s1] := flip[1, "share1"] xor flip[1, "share2"] xor s[1, "s:mysecret"] \end{verbatimtab}
  }
\end{example}

@@

For full details of the GMW protocol the reader is referred to
\cite{evans2018pragmatic}. Our implementation libary is shown in
Figure \ref{fig-gmw}, with type signatures for the library functions
shown in Figure \ref{fig-gmw-types}. We show the And gate since it is
an interesting component. The Figure includes the
following top-level functions:
\begin{itemize}
\item \ttt{encodegmw}: This function encodes client 1's and client 2's
  secret bits called $\ttt{s[1,"s1"]}$ and $\ttt{s[1,"s2"]}$ into two
  distinct wire values (pairs of shares).
\item \ttt{andgmw}: This function defines the gate $\ttt{"g"}$, the
  identifier $\ttt{"g"}$ being used to distinguish randomness used
  within.  In our version client 1 builds the output table (using
  \ttt{andtablegmw})and transfers the correct output share to client 2
  using 1-out-of-4 OT as per standard GMW protocol.
\item \ttt{decode}: This function decodes and publishes a wire value
  by $\ttt{xor}$ing the shares. Note that this requires both client 1
  and 2 to publicize their shares.
\end{itemize}
\begin{example}
  \label{example-gmw-andcircuit}
The following program uses our GMW library to define
a circuit with a single And gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively. 
{\small
  \begin{verbatimtab}
  let ss = encodegmw("s1","s2") in v[0,"output"] := decode(andgmw(0,ss.shares1,ss.shares2)) \end{verbatimtab}
}
\end{example}

@@

\emph{Wire labels} are fundamental to YGC, and essentially represent
gate output values in an encrypted form. In our definition, wire
labels are represented by records $\ttt{\{ k = }\beta_1\ttt{; p =
}\beta_2\ttt{ \}}$, where $\ttt{k}$ is the \emph{key bit} and
$\ttt{p}$ is the \emph{pointer bit}, and $\beta_1$ and $\beta_2$ are
flips. Flips in each output wire label are owned by the garbler and
are unique per gate by definition of their identifying string, and the
representation of $0$ is the negation of $1$. For example, here is the
representation of 1 and 0 respectively in the output wire label for a
hypothetical gate 6:
{\small
  \begin{mathpar}
    \ttt{\{ k = flip[2,"gate:6.k"]; p =  flip[2,"gate:6.p"]] \}}

    \ttt{\{ k = not flip[2,"gate:6.k"]; p =  not flip[2,"gate:6.p"]] \}}
  \end{mathpar}
}
In our implementation, gates are wired together using gate
identifiers, which are strings $w$. Top-level functionality
shown in Figure \ref{fig-ygc-lib} includes:
\begin{itemize}
\item \ttt{owl}: This function returns the output wire label for any
  gate identified by \ttt{gid}.
\item \ttt{andgate}: This defines a subprotocol for the garbler
  to define a garbled gate $\ttt{gid}$ with input wires from gates
  $\ttt{ga}$ and $\ttt{gb}$. The garbler generates keys and garbles
  the rows in YGC fashion, them with client $1$ in
  views in a standard form. For example, the view for
  a hypothetical gate 6, row 2 garbled truth table is $\ttt{v[1,gate:6tt2]}$.
  We note that garbled gates of other binary operators can be obtained with
  replacement of $\ttt{andtable}$ with appropriate garbled table definitions. 
\item \ttt{evalgate}: This defines a subprotocol for the evaluator to
  evaluate gate $\ttt{gid}$ given input wire values $\ttt{wva}$ and
  $\ttt{wvb}$.
\item \ttt{andygc}: This composes the garbler and evaluator subprotocols
  for construction and evaluation of an And gate. 
\item \ttt{garbledecode} and \ttt{evaldecode}: The former function
  defines the garbler's protocol for encrypting the circuit
  output from final gate $\ttt{gid}$, and the latter defines
  the evaluator's output decryption protocol. These are composed with \ttt{decodeygc}.
\item \ttt{encodegmw}: This defines the initial phase of the protocol,
  where the evaluator receives the wire value from their own
  secret $\sx{1}{sa}$ via $\ttt{OT}$, and the garbler communicates
  the wire value for their own secret $\sx{2}{sb}$ directly.
\end{itemize}
We provide more code details in Appendix \ref{section-ygc}, Figures
\ref{fig-ygc-aux} and \ref{fig-ygc-gates}, and complete code in our
online repository.
\begin{example}
  \label{example-ygc-andcircuit}
The following program uses our YGC library to define
a circuit with a single and gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively. 
{\small
\begin{verbatimtab}
  let secrets = encode("s1","s2") in
  v[0,output] := decode(andgg("0", secrets.wv1, secrets.wv2)) \end{verbatimtab}
}
%\begin{verbatimtab}
%  andgate(0,s1,s2);
%  garbledecode(0);
%  let secrets = encode(s1,s2) in
%  v[0,output] := decode(evalgate(0, secrets.wv1, secrets.wv2))
%\end{verbatimtab}
\end{example}
